Connecting the Popularity Adjusted Block Model to the Generalized Random Dot Product Graph for Clustering and Parameter Estimation

### 2020-10-08 summary.Rmd
updated final real data example

* Number of underlying communities $K = 2, 4, 8$
* Mixture parameters $\alpha_k = 1 / K$ for $k = 1, ..., K$
* Within-group popularities $\lambda^{(kk)} \stackrel{iid}{\sim} Beta(2, 1)$
* Between-group popularities 
$\lambda^{(kl)} \stackrel{iid}{\sim} Beta(1, 2)$ for $k \neq l$

@@

```{r}
import::here(cluster.pabm, plot.A, .from = '~/dev/pabm-grdpg/functions.R')

@@

In the third example,

```{r, cache = FALSE, fig.cap = 'Adjacency matrix of the Karnataka villages data, arranged by the clustering produced by Algorithm 2 (left) and results of \\citet{fosdick2016multiresolution} (right).', fig.height = 2}
hh <- readRDS('data/village-hh-59.rds')
A.hh <- hh$A
z.hh <- hh$z
K <- 6
zhat.hh <- cluster.pabm(A.hh, K, 
                        use.all = TRUE, normalize = FALSE, p = K, q = 0)

zhat.mres <- readRDS('data/mres-result.rds')

gridExtra::grid.arrange(plot.A(A.hh, zhat.hh), 
                        plot.A(A.hh, zhat.mres),
                        ncol = 2)
```

>>>>

* Number of underlying communities $K = 2, 4, 8$
* Mixture parameters $\alpha_K = 1 / K$ for $k = 1, ..., K$
* Community labels 
$z_k \stackrel{iid}{\sim} Multinomial(\alpha_K, ..., \alpha_K)$
* Within-group popularities $\lambda^{(kk)} \stackrel{iid}{\sim} Beta(2, 1)$
* Between-group popularities 
$\lambda^{(kl)} \stackrel{iid}{\sim} Beta(1, 2)$ for $k \neq l$

@@

```{r}
import::here(cluster.pabm, ssc, plot.A, .from = '~/dev/pabm-grdpg/functions.R')

@@

In the third example, we consider the Karantaka villages data studied by 
\citet{DVN/U3BIHX_2013}. For this example, we chose the `visitgo` network from 
village 12 at the household level. The label of interest is the religious 
affiliation. The network was truncated to religions "1" and "2", and vertices 
of degree 0 were removed. The resulting network has 141 vertices.

```{r, cache = FALSE, fig.cap = 'Adjacency matrix of the Karnataka villages data, arranged by the clustering produced by Algorithm 2 (left) and sparse subspace clustering (right).', fig.height = 2, fig.width = 6, eval = TRUE}
hh <- readRDS('data/village-hh-12.rds')
A.hh <- hh$A
z.hh <- hh$z
K <- 2
zhat.hh <- cluster.pabm(A.hh, K,
                        use.all = TRUE, normalize = FALSE, p = 3, q = 1)
zhat.hh.ssc <- ssc(A.hh, K, lambda = .1)

gridExtra::grid.arrange(plot.A(A.hh, zhat.hh),
                        plot.A(A.hh, zhat.hh.ssc),
                        ncol = 2)
```

```{r, eval = TRUE}
hh.acc <- mean(zhat.hh == z.hh)
hh.acc <- ifelse(hh.acc < .5, 1 - hh.acc, hh.acc)
hh.acc.ssc <- mean(zhat.hh.ssc == z.hh)
hh.acc.ssc <- ifelse(hh.acc.ssc < .5, 1 - hh.acc.ssc, hh.acc.ssc)

knitr::kable(data.frame(method = c('Algorithm 2', 'SSC'),
                        accuracy = round(c(hh.acc, hh.acc.ssc), 3)))
```
